WordRec Experiment

### 2017-02-02 data and analysis/analysis3.Rmd
exp3

Data, and exclusion

@@

d <- read_delim("data_experiment2_complete.txt", delim = " ") %>%
  filter(ID !="AR1IWBDA7MC86", ID !="A3GOKNZGZGHL45") %>% #took the experiment twice
  filter(type == "Task", problem=="No")  %>% #had a technical problem during the experiment
  filter(score > 0.5)  #got more less than 50% correct on the training trials

@@

ggplot(joint, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  #geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                 # position = position_dodge(width = .1), size=0.3) + 
  geom_point(size=2) +
  geom_line(size=0.7) + 
  geom_line(data = sounds, aes(col = 1), col = "black",size=0.7) + 
  #geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
                             #        col = 1), col = "black", size=0.4)+
  geom_hline(data = concepts, aes(yintercept=mean, col = factor(concept_dist)), lty = 2)+
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

@@

Fit the models.
```{r}

@@

```
Modalitiy preference plot
```{r}
#I make a data frame 
model = c('baseline', 'fit')
mean=c(1.64,1.45)
ci_low=c(1.24,1.29)
ci_up=c(2.02,1.65)
pref=data.frame(mean, ci_low, ci_up,model)

@@

```
Analysis of the unimodal cases.
```{r}

@@

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=uniV_nl,aes(x=xV_nl, y=yV_nl), col='black')+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+theme(aspect.ratio = 0.7)
  #stat_function(fun = Logistic_v, colour="red")

@@

The bimodal case, all plots
```{r}

@@

Modality preference
```{r}

>>>>

The following analysis is done using pilot data with 25 subjects.

We plan to collect data for 100 subjects

Data.

@@

#Skip the pre task trials 
#Filter subjects who had no technical problem
#Select subjects who got more than 50% correct answers on the pre task trials

d <- read_delim("data_experiment3.txt", delim = " ") %>%
  filter(type == "Task", problem=="No") %>%
  filter(score > 0.5)
```

@@

ggplot(joint, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1), size=0.3) + 
  geom_line(lty = 2) + 
  geom_line(data = sounds, aes(col = 1), col = "black") + 
  geom_pointrange(data = sounds, aes(ymin = ci_lower, ymax = ci_upper, 
                                     col = 1), col = "black", size=0.4)+
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

@@

```
Fit the models.
```{r}

@@

```{r}
#I make a data frame 
model = c('baseline', 'fit')
mean=c(0.84,0.53)
ci_low=c(0.68,0.46)
ci_up=c(1.04,0.60)
pref=data.frame(mean, ci_low, ci_up,model)

@@

Analysis of the unimodal cases.
```{r}

@@

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=uniV_nl,aes(x=xV_nl, y=yV_nl), col='black')+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+theme(aspect.ratio = 0.7)
  #stat_function(fun = Logistic_v, colour="red"))

@@

The bimodal case

@@

The modality dominance
```{r}
